---
title: "Data 607 - Project 3 - Research"
author: "Glen Dale Davis, Coco Donovan, Alex Khaykin, Mohamed Hassan-El Serafi, Eddie Xu"
date: "2023-02-21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load the Required Packages:

Below, the packages required for data analysis and visualization are loaded.

```{r packages, warning = FALSE, message = FALSE}
library(tidyverse)
library(magrittr)
library(DBI)
library(dbplyr)
library(RMariaDB)
library(data.table)
library(stopwords)
library(tidytext)
library(RColorBrewer)
library(DT)
library(wordcloud)

```

## State the Research Question: 

W. Edwards Deming said, “In God we trust, all others must bring data.” Below, we will use data to explore the question, **“Which are the most valued data science skills?”**

## Connect to the SQL Data Base:

```{r db_con1}
con <- DBI::dbConnect(
  RMariaDB::MariaDB(),
  dbname = "dat_sci_jobs",
  username = "root",
  password = as.character(read.table("sql_db.txt", header = FALSE)),
  host = "35.227.102.234")

```

## Read from the SQL Data Base and Disconnect:

```{r db_write1}
tables <- dbListTables(con)
jobs_df <- dbReadTable(con, "_Jobs")
datatable(jobs_df[, -3], options = list(pageLength = 25))
dbDisconnect(con)

```

## Create a Data Frame of Jobs Found via RSS Feed By Combining CSV Files and Removing Duplicates:

```{r jobs_df}

completed_files <- readLines("completed_files.txt")

url_base <- "https://raw.githubusercontent.com/geedoubledee/data607_project3/main/"

new_jobs_df <- as.data.frame(matrix(nrow = 0, ncol = 11))
files <- list.files(pattern = "_feeds_.*csv$")

for (i in 1:length(files)){
    if (!(files[i] %in% completed_files)){
        file <- paste(url_base, files[i], sep = "")
        csv <- read.csv(file = file, header = TRUE)
        new_jobs_df <- rbind(new_jobs_df, csv)
        completed_files <- append(completed_files, files[i])
    }
}

new_jobs_df2 <- as.data.frame(matrix(nrow = 0, ncol = 10))
files <- list.files(pattern = "_linkedin_.*csv$")

for (i in 1:length(files)){
    if (!(files[i] %in% completed_files)){
        file <- paste(url_base, files[i], sep = "")
        csv <- read.csv(file = file, header = TRUE)
        new_jobs_df2 <- rbind(new_jobs_df2, csv)
        completed_files <- append(completed_files, files[i])
    }
}

writeLines(completed_files, "completed_files.txt")

new_jobs_df <- new_jobs_df[!duplicated(new_jobs_df), ]
new_jobs_df2 <- new_jobs_df2[!duplicated(new_jobs_df2), ]

```

## Remove Unnecessary Columns in Jobs Data Frame and Rearrange Remaining Columns to Prepare the Data for the SQL Data Base:

```{r jobs_df_minimize}
if (nrow(new_jobs_df) > 0){
    new_jobs_df <- subset(new_jobs_df, select = -c(X, author, summary,
        content, extracted_content_url, published, created_at))
    cols <- c("Job_id", "Site_id", "Job_title", "Job_url")
    colnames(new_jobs_df) <- cols
    Job_company <- as.data.frame(matrix(NA, nrow = nrow(new_jobs_df),
                                   ncol = 1))
    colnames(Job_company) <- "Job_company"
    Job_location <- as.data.frame(matrix(NA, nrow = nrow(new_jobs_df),
                                    ncol = 1))
    colnames(Job_location) <- "Job_location"
    new_jobs_df <- cbind(new_jobs_df, Job_company, Job_location)
    rownames(new_jobs_df) <- NULL
    new_jobs_df <- new_jobs_df[c("Job_id", "Job_title", "Job_url",
                                 "Job_company", "Job_location", "Site_id")]
    new_jobs_df %<>%
        mutate(Job_complete = 0)
}

if (nrow(new_jobs_df2) > 0){
    new_jobs_df2 <- subset(new_jobs_df2, select = -c(X, job_url, company_url,
        linkedin_company_url_cleaned, posted_date, normalized_company_name))
    cols <- c("Job_url", "Job_company", "Job_title", "Job_location")
    colnames(new_jobs_df2) <- cols
    Job_id <- as.data.frame(matrix(NA, nrow = nrow(new_jobs_df2),
                                   ncol = 1))
    colnames(Job_id) <- "Job_id"
    Site_id <- as.data.frame(matrix(1001, nrow = nrow(new_jobs_df2),
                                    ncol = 1))
    colnames(Site_id) <- "Site_id"
    new_jobs_df2 <- cbind(new_jobs_df2, Job_id, Site_id)
    rownames(new_jobs_df2) <- NULL
    new_jobs_df2 <- new_jobs_df2[c("Job_id", "Job_title", "Job_url",
                                   "Job_company", "Job_location", "Site_id")]
    new_jobs_df2 %<>%
        mutate(Job_complete = 0)
}

if (nrow(new_jobs_df) > 0){
    jobs_df <- rbindlist(list(jobs_df, new_jobs_df))[!duplicated(Job_url)]
}
if (nrow(new_jobs_df2) > 0){
    jobs_df <- rbindlist(list(jobs_df, new_jobs_df2))[!duplicated(Job_url)]
}
jobs_df %<>%
    mutate(Job_id = row_number())

```

## Scrape Each Unique Job Listing URL:

```{r scrape, warning = FALSE, message = FALSE}

for (i in 1:nrow(jobs_df)){
    httr::user_agent("Glen Davis")
    if (jobs_df[i, 7] == 0){
        dat <- try(xml2::read_html(jobs_df$Job_url[[i]]), silent = TRUE)
        if (inherits(dat, "try-error", which = FALSE)){
            jobs_df[i, 7] <- -1
            next
        }
    }else{
        next
    }
    if (jobs_df[i, 6] == 2594160){ #ai-jobs.net is source
        desc <- xml2::xml_find_all(
            dat, "//div[contains(@id, 'job-description')]")
    }
    else if (jobs_df[i, 6] == 977141){ #python.org is source
        desc <- xml2::xml_find_all(
            dat, "//div[contains(@class, 'job-description')]")
    }
    else if (jobs_df[i, 6] == 2594162){ #careercast it & eng is source
        desc <- xml2::xml_find_all(
            dat, "//div[contains(@class, 'arDetailDescriptionRow')]")
    }
    else if (jobs_df[i, 6] == 1378327){ #jobs for r-users is source
        desc <- xml2::xml_find_all(
            dat, "//div[contains(@class, 'section_content')]")
    }
    else if (jobs_df[i, 6] == 2593879){ #Indeed is source
        jobs_df[i, 7] <- -1
        next
    }
    else if (jobs_df[i, 6] == 2594166){ #Open Data Science is source
        desc <- xml2::xml_find_all(
            dat, "//div[contains(@class, 'job-desc')]")
    }
    else if (jobs_df[i, 6] == 2594174){ #MLconf is source
        desc <- xml2::xml_find_all(
            dat, "//div[contains(@class, 'job_description')]")
    }
    else if (jobs_df[i, 6] == 1001){ #Linkedin is source
        jobs_df[i, 7] <- -1
        next
    }
    
    desc <- xml2::xml_text(desc)
    fn <- paste(jobs_df[i, 1], ".txt", sep = "")
    writeLines(desc, con = fn)
    jobs_df[i, 7] <- 1
}

```

## Manual Data Collection for LinkedIn:

```{r manual1}
manual <- jobs_df %>%
    filter(Job_complete == -1 & Site_id == 1001)
write.csv(manual, "manual.csv", row.names = FALSE)

```

We look up the job descriptions for the job listings in the manual.csv file manually, and we save them as column eight of a manual_edited.csv file. If we find a job description, we change the Job_complete value to 1. If we don't, we can just delete that row. If a previous file exists, we save over it. We then upload the saved manual_edited.csv file to github before continuing. 

```{r manual2}
file <- "https://raw.githubusercontent.com/geedoubledee/data607_project3/main/manual_edited.csv"

manual_edited <- read.csv(file = file, header = TRUE)
for (i in 1:nrow(manual_edited)){
    job_id <- manual_edited[i, 1]
    if (jobs_df[job_id, 7] != 1){
        job_desc <- manual_edited[i, 8]
        jobs_df[job_id, 7] <- manual_edited[i, 7]
        fn <- paste(job_id, ".txt", sep = "")
        writeLines(job_desc, con = fn)
    }
}

```

## Add Previously Scraped (Nov. 2022) Data for Indeed Jobs (Source: Kaggle)

```{r kaggle_indeed}

completed_files <- readLines("completed_files.txt")

if (!("data_science_jobs_indeed_usa.csv" %in% completed_files)){
    file <- "https://raw.githubusercontent.com/geedoubledee/data607_project3/main/data_science_jobs_indeed_usa.csv"
    kaggle_indeed <- read.csv(file = file, header = TRUE)
    kaggle_indeed <- subset(kaggle_indeed, select = -c(1, 5, 6, 7, 8))
    cols <- c("Job_title", "Job_company", "Job_location", "Job_url",
              "Job_description")
    colnames(kaggle_indeed) <- cols
    ids <- seq((nrow(jobs_df) + 1), (nrow(jobs_df) + nrow(kaggle_indeed)))
    Job_id <- as.data.frame(matrix(ids, nrow = nrow(kaggle_indeed),
                                   ncol = 1))
    Site_id <- as.data.frame(matrix(2593879, nrow = nrow(kaggle_indeed),
                                    ncol = 1))
    Job_complete <- as.data.frame(matrix(0, nrow = nrow(kaggle_indeed),
                                         ncol = 1))
    colnames(Site_id) <- "Site_id"
    colnames(Job_id) <- "Job_id"
    colnames(Job_complete) <- "Job_complete"
    kaggle_indeed <- cbind(kaggle_indeed, Job_id, Site_id, Job_complete)
    rownames(kaggle_indeed) <- NULL
    kaggle_indeed <- kaggle_indeed[c("Job_id", "Job_title", "Job_url",
                                     "Job_company", "Job_location",
                                     "Site_id", "Job_complete",
                                     "Job_description")]
    jobs_df <- rbind(jobs_df, subset(kaggle_indeed, select = 1:7))
    for (i in 1:nrow(kaggle_indeed)){
        job_id <- kaggle_indeed[i, 1]
        job_desc <- kaggle_indeed[i, 8]
        jobs_df[job_id, 7] <- 1
        fn <- paste(job_id, ".txt", sep = "")
        writeLines(job_desc, con = fn)
    }
    write("data_science_jobs_indeed_usa.csv", file = "completed_files.txt",
          append = TRUE)
}

```

## Connect to the SQL Data Base:

```{r db_con2}
con <- DBI::dbConnect(
  RMariaDB::MariaDB(),
  dbname = "dat_sci_jobs",
  username = "root",
  password = as.character(read.table("sql_db.txt", header = FALSE)),
  host = "35.227.102.234")

```

## Write to the SQL Data Base Only If There Were Changes and Disconnect:

```{r db_write2}
tables <- dbListTables(con)
copy <- dbReadTable(con, "_Jobs")

if (!identical(jobs_df, copy)){
    dbWriteTable(con, "_Jobs", jobs_df, overwrite = TRUE)
}

dbDisconnect(con)

```

## Set Up a Text Data Frame from the TXT Job Description Files

```{r tidytext_setup}

files <- list.files(pattern = "^[1-9]+.*txt$")
if (length(files) > 0){
    file.copy(from = paste0(getwd(), "/", files),
              to = paste0(getwd(), "/jobs-txt/", files))
    file.remove(from = paste0(getwd(), "/", files))
}

files <- list.files(path = paste0(getwd(), "/jobs-txt/"),
                    pattern = "^[1-9]+.*txt$")

cols <- c("Text", "Job_id", "Line")

completed_txt_files <- readLines("completed_txt_files.txt")
if (length(completed_txt_files) == 0){
    text_df <- as.data.frame(matrix(nrow = 0, ncol = 3))
    colnames(text_df) <- cols
}else{
    my_url <- "https://raw.githubusercontent.com/geedoubledee/data607_project3/main/text_df.csv"
    text_df <- read.csv(file = my_url, header = TRUE)
}

url_base <- "https://raw.githubusercontent.com/geedoubledee/data607_project3/main/jobs-txt/"

for (i in 1:length(files)){
    if (!(files[i] %in% completed_txt_files)){
        file <- paste(url_base, files[i], sep = "")
        job_id <- str_replace(files[i], ".txt", "")
        lines <- readLines(file)
        for (j in 1:length(lines)){
            col2 <- matrix(job_id, nrow = length(lines), ncol = 1)
            col3 <- matrix(1:length(lines),
                           nrow = length(lines),
                           ncol = 1)
        }
        addition <- cbind(lines, col2, col3)
        colnames(addition) <- cols
        text_df <- rbind(text_df, addition)
        write(files[i], file = "completed_txt_files.txt", append = TRUE)
    }
}

rownames(text_df) <- NULL
write.csv(text_df, "text_df.csv", row.names = FALSE)

```

## Analyze the Text Data Frame with Tidytext

```{r tidytext_analysis}

tidy_text_df_words <- text_df %>%
    unnest_tokens(word, Text)

tidy_text_words_analysis <- tidy_text_df_words %>%
    anti_join(get_stopwords()) %>%
    group_by(word) %>%
    summarize(term_freq = n(), doc_count = n_distinct(Job_id)) %>%
    arrange(desc(doc_count))
    
datatable(tidy_text_words_analysis, options = list(pageLength = 25))

tidy_text_words_analysis %>%
    with(wordcloud(word, doc_count, max.words = 50))

tidy_text_df_bigrams <- text_df %>%
    unnest_tokens(bigram, Text, token = "ngrams", n = 2)

tidy_text_bigrams_analysis <- tidy_text_df_bigrams %>%
    group_by(bigram) %>%
    summarize(term_freq = n(), doc_count = n_distinct(Job_id)) %>%
    arrange(desc(doc_count))

datatable(tidy_text_bigrams_analysis, options = list(pageLength = 25))

tidy_text_bigrams_analysis %>%
    with(wordcloud(bigram, doc_count, max.words = 50))

tidy_text_df_trigrams <- text_df %>%
    unnest_tokens(trigram, Text, token = "ngrams", n = 3)

tidy_text_trigrams_analysis <- tidy_text_df_trigrams %>%
    group_by(trigram) %>%
    summarize(term_freq = n(), doc_count = n_distinct(Job_id)) %>%
    arrange(desc(doc_count))

datatable(tidy_text_trigrams_analysis, options = list(pageLength = 25))

tidy_text_trigrams_analysis %>%
    with(wordcloud(trigram, doc_count, max.words = 50))



```


